%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Sumit Singh
\documentclass[margin,line]{resume}
\usepackage{url}
\usepackage{enumerate}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Sumit Singh}
\begin{resume}

    % Contact
    \section{\mysidestyle Contact}
    	542/57, New Haiderganj, Post Chowk, Lucknow, India.\\
    	Email: ssumit.cse@gmail.com\\
    	Mobile: +91-8860565677\\
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
    Year & Degree & Institution (Board) & CGPA/\% \\ \hline
    2012 & Masters (CSE) & Indian Institute of Technology, Kanpur & 9.0/10.0 \\ \hline
    2010 & B.E. (CSE) & Birla Institute of Technology, Mesra & 7.53/10.0 \\ \hline
    2006 & 12th & City Montessori School, Lucknow(ISC) & 84.6 \\   \hline
    \end{tabular}
\end{center}


%__________________________________________________________________________________________________________________


    \section{\mysidestyle Current Work}

\textit{Software Developer on Android Platform - Directi} \\
Time: Feb 14 onwards.\\
Product: voip client.\\
\begin{itemize}
	\item worked in Java, JNI, C, XML with emphasis on good code design.
        \item developed initial prototype alone.
        \item working in a team of 2.
	\item use continuous build system and analytics.
	\item switched from IntelliJ + Ant to Android Studio + Gradle.
 \end{itemize}

\textit{Software Developer on Android Platform - Directi} \\
Time: Sep 13 - Jan 14.\\
Product: talk.to (chatting client).\\
\begin{itemize}
\item Languages: Java, XML, (occasional Python scripts).\\
\item Tools: Ant, Android Perfomance tools (e.g. monitor), Java profiler (YJP).\\
\item Test: Unit testing(junit) and functional testing (android specific).
 \end{itemize}

\textit{Repositories at https://github.com/ssumit/}\\
 \begin{itemize}
        \item jSSL - tranpost agnostic SSL convenience library.
        \item jSession - towards transport agnostic session maintainance.
        \item droidMedia, notifications - android library.
 \end{itemize}

\textit{Training project at Directi}\\
Time: Jul 13 - Sep 13.
Product: similar to twitter - web client and server.\\
 \begin{itemize}
\item Languages: Java, Javascript.
\item Build Tool: Maven.
\item Database: PostgreSQL, Redis.
\item Other: Java Spring MVC framework, Apache http server.  
 \end{itemize}


%__________________________________________________________________________________________________________________


    \section{\mysidestyle Selected Research Work}
\vspace{-2mm}
Sumit Singh and Shashank K Mehta, \textit{ "An Improved Approximation ratio for Prize Collecting Steiner Forest Problem in Node Weighted Planar Graphs"}, part of M.Tech thesis.

\vspace{-2mm}
Pawan Aurora, Sumit Singh and Shashank K Mehta, \textit{"Partial Dergree Bounded Edge Packing Problem with Arbitary bounds"}, Proceedings of FAW-AAIM, Lecture Notes in Computer Science, vol 7924, pp 24-35, 2013. 

\vspace{-2mm}
Sumit Singh, \textit{"A Local Approach for Identifying Clusters in Networks."}, arxiv:1203.4685, 2012.

\vspace{-2mm}
Sumit Singh and Ayushi Garg, \textit{"Towards The Adaptive Questionnaire Generation Using Soft Computing"}, Proceedings of NaBIC, pp 806-811, 2009.


    %__________________________________________________________________________________________________________________

    \section{\mysidestyle M. Tech Thesis}
The thesis was in the area of approximation algorithms under the guidance of Prof. Shashank K Mehta. 
We mostly worked on upper bounds for mainly graph based problems. We were able to improve the state of the art in  the two of the three problems that we looked at (at the time of thesis defence).
   
   
   %__________________________________________________________________________________________________________________

\vspace{8mm}
    \section{\mysidestyle Key Academic Projects}
\renewcommand{\labelitemi}{$\bullet$}
	\textit{Prestige Evaluation and Finding Group Structure in Networks:} 
	\begin{itemize}
	\item
	This work was started as a part of the Department of Science and Technology sponsored project and involved implementing various graph algorithms and heuristics. 
	\item The overall aim of the project was to monitor web-based user forums/channels and identify the communities in any social network. 
	\item We were able to identify the hierarchical community structures which further lead to discover prestige of each member. 
	\item The work was extended to find the overlapping communities which real world do exhibit.
	\item The size of datasets consisted of around 30 million nodes. 
\end{itemize}

\vspace{-2mm}
	\textit{Path Profiling Problem:} 
	\begin{itemize}
	\item We worked on a variant of path profiling problem which is a standard problem in the area of compilers.
	\item We came up with some heuristics.
	\end{itemize}

\vspace{-2mm}
	\textit{Autonomous Pseudo-vision Path Detector System:} 
	\begin{itemize}
	\item We built a smart robot which could identify object boundaries and could itself find out the path to the destination.
	\item  It also identified objects based on their feature set which could then be used as future destination. 
	\item My major contributions included implementing image-processing algorithms and decision-making algorithms.
	\end{itemize}

\vspace{-2mm}
	\textit{CUDA-Based High Performance Computing:} 
	\begin{itemize}
	\item It included implementation of parallel algorithms on CUDA to compare large images and calculate histogram (as part of course work).
	\item The results obtained using CUDA were compared with the results obtained on multi-processor systems using MPI.
	\end{itemize}	

    %__________________________________________________________________________________________________________________
    % Courses

    \section{\mysidestyle Academic Positions of Responsibility} 
	Teaching Assistant for Algorithms II (Jan 12 - May 12).\\ 
	Teaching Assistant for Randomized Algorithms (July 11 - Dec 11).\\ 
	Teaching Assistant for C Programming Lab (July 10 - May 11).\\
    %__________________________________________________________________________________________________________________
    % Technical Skills
    \section{\mysidestyle Technical \quad Skills} 
	Programming Languages: C, Java, Python(learning).\\
	Library/software: MPI, MATLAB. \\
	Architecture: CUDA. \\
	Databases : Relational - SQL, KeyValue - Redis. \\
    %__________________________________________________________________________________________________________________
    % Other
    \section{\mysidestyle Conference/ Schools Attended}
    Summer School on Distributed Algorithms, Systems and Programming, conducted by Microsoft Research and IISC, Bangalore in 2012. \\
    Attended a short course on software architecture by Prof. Philip Dugerdil in 2012. \\
    NaBiC 2009 - conference on soft computing. \\
    ICMCM 2009 - conference on mathematical models. \\

    %__________________________________________________________________________________________________________________
    % Hobbies
    \section{\mysidestyle Interest \& Hobbies}
    playing snooker and basketball.\\
    listening music.\\ 

\end{resume}
\end{document}
%______________________________________________________________________________________________________________________
% EOF

